Data Exploration

### 2024-02-08 analysis/documents/2-data-exploration.qmd
update

By cameras

```{r, fig.height=20, fig.width=8}
#| label: camdep-plot

cam_dep_data_with_status <- cam_dep_data |> 
  dplyr::mutate(status = ifelse(date_deployed < date_retrieved, "valid", "invalid")) |> 
  dplyr::mutate(status = ifelse(is.na(status), "invalid", status))

cam_dep_data_with_status |> 
  ggplot2::ggplot() +
  ggplot2::geom_segment(ggplot2::aes(x = date_deployed, y = camera_id, 
                                     xend = date_retrieved, yend = camera_id,
                                     color = status)) +
  ggplot2::geom_point(ggplot2::aes(x = date_deployed, y = camera_id, 
                                   color = status)) + 
  ggplot2::geom_point(ggplot2::aes(x = date_retrieved, y = camera_id, 
                                   color = status)) + 
  ggplot2::scale_color_discrete(type = c("#E69F00","#56B4E9")) +
  ggplot2::theme_bw()
```

By sites

```{r, fig.height=40, fig.width=8}
cam_dep_data_with_status |> 
  ggplot2::ggplot() +
  ggplot2::geom_segment(ggplot2::aes(x = date_deployed, y = site_id,
                                     xend = date_retrieved, yend = site_id,
                                     color = status), alpha = 0.15, linewidth = 3) +
  ggplot2::geom_point(ggplot2::aes(x = date_deployed, y = site_id,
                                   color = status)) +
  ggplot2::geom_point(ggplot2::aes(x = date_retrieved, y = site_id,
                                   color = status)) +
  ggplot2::geom_text(ggplot2::aes(x = date_deployed-40, y = site_id,
                                  label = camera_id,
                                  color = status), size = 3) +
  ggplot2::scale_color_discrete(type = c("#E69F00","#56B4E9")) +
  ggplot2::theme_bw()
```

With image density

```{r, fig.height=40, fig.width=8}
cam_dep_data_with_status |> 
  ggplot2::ggplot(ggplot2::aes(x = date_deployed, y = reorder(site_id, 
                                                              date_deployed,
                                                              decreasing = TRUE))) +
  ggplot2::geom_segment(ggplot2::aes(xend = date_retrieved, yend = site_id,
                                     color = status), alpha = 0.15, linewidth = 3) +
  ggplot2::geom_point(ggplot2::aes(x = date_deployed, y = site_id,
                                   color = status)) +
  ggplot2::geom_point(ggplot2::aes(x = date_retrieved, y = site_id,
                                   color = status)) +

  ggplot2::geom_point(data = image_data,
                      ggplot2::aes(x = date_time, y = site_id), 
                      color = "firebrick", size = 0.5) +

  ggplot2::geom_text(ggplot2::aes(x = date_deployed-60, y = site_id,
                                  label = camera_id,
                                  color = status), size = 3) +
  ggplot2::scale_color_discrete(type = c("#E69F00","#56B4E9")) +
  ggplot2::theme_bw()
```

Sorted by deployment date

>>>>

Cameras, Sorted by deployment date, with associated site labelled.
